MSPMS Report

### 2024-09-04 inst/rmarkdown/templates/mspms_report/skeleton/skeleton.Rmd
fixes

@@

**Figure 3.** Here a PCA of the experiment is displayed. The color represents time, while shape and linetype of eclipse (if there are enough points to calculate) represents condition.

@@

**Figure 4.** Here an interactive heatmap of the experiment is displayed. Mouse over to see more information on each cell. Column side colors represent condition and time.

@@

```{r}
sig = t2 %>% 
  filter(p.adj <= 0.05, log2fc >3)

>>>>

```{r}
plot_rt_qc(prepared_data,design_matrix)
```

**Figure 3.** Here the distribution of peptides detected per retention time are 
shown for each group.

@@

**Figure 4.** Here a PCA of the experiment is displayed. The color represents time, while shape and linetype of eclipse (if there are enough points to calculate) represents condition.

@@

**Figure 5.** Here an interactive heatmap of the experiment is displayed. Mouse over to see more information on each cell. Column side colors represent condition and time.

@@

```{r}
sig = t2 %>% 
  dplyr::filter(p.adj <= 0.05, log2fc >3)
